%======================
% Packages
%======================
\documentclass[a4paper,11pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage[none]{hyphenat}


%======================
% font
%======================
\usepackage{fontspec}
\setmainfont{Times New Roman}

% Customize section spacing
\titlespacing{\section}{0pt}{6pt}{2pt}
\titlespacing{\subsection}{0pt}{4pt}{2pt}

% Remove section numbering
\titleformat{\section}{\large\bfseries}{}{0em}{}

% No indentation
\setlength{\parindent}{0pt}

\begin{document}

%======================
% Name and Contact Info
%======================
\begin{center}
    {\Huge \textbf{Ethan Childs}} \\
    \vspace{0pt}
    Dallas, Texas
    \,\textbar\, 
    817-675-9073 
    \,\textbar\,
    \href{mailto:EthanChildsbc@gmail.com.com}{EthanChildsbc@gmail.com}
    \,\textbar\, 
    \href{https://linkedin.com/in/ethanchilds}{linkedin.com/in/ethanchilds}
    \,\textbar\, 
    \href{https://github.com/Ethan-Childs}{github.com/Ethan-Childs}
    
\end{center}
\vspace{-0.9em}
%======================
% Education
%======================
\section*{Education}
\vspace{-0.8em}
\rule{\linewidth}{2pt}
\textbf{Texas Tech University} \hfill Lubbock, Texas 

\textit{Bachelor of Science} \hfill Expected Graduation: May 2026

Major: Computer Science

Minor: Mathematics
\vspace{-0.8em}
\begin{itemize}
    \item GPA: 3.62
    \vspace{-0.8em}
    \item President’s List: Spring 2023, Fall 2024
    \vspace{-0.8em}
    \item Dean’s List: Fall 2021, Spring 2022
\end{itemize}
\vspace{-0.5em}
\vspace{-0.5em}
%======================
% Work Experience
%======================
\section*{Work Experience}
\vspace{-0.8em}
\rule{\linewidth}{2pt}

\textbf{Data Analyst} \hfill Lubbock, Texas

\textit{NemaLife inc.} \hfill January 2025 - Current
\vspace{-0.8em}
\begin{itemize}
    \item Trained the company AI to enhance the accuracy of pharmaceutical test data on C. \textit{elegans}.
    \vspace{-0.8em}
    \item Performed video annotations to ensure accurate data was presented to clientele.
    \vspace{-0.8em}
    \item Cataloged and managed over 1000 annotation and AI statistics in Excel Spreadsheets.
    \vspace{-0.8em}
    \item Coordinated with 10 other Data Analysts to ensure project deadlines were met on time. 
\end{itemize}
\vspace{-0.8em}
\textbf{Sports Statistician} \hfill Lubbock, Texas

\textit{Genius Sports (Seasonal)} \hfill October 2024 - December 2024
\vspace{-0.8em}
\begin{itemize}
    \item Updated live game statistics for Texas Tech football games on company software to determine betting odds.
    \vspace{-0.8em}
    \item Compiled reports at the end of the game including average stats and future projections for key players.
    \vspace{-0.8em}
    \item Worked diligently to have live game statistics updated before the start of the next sequence.
\end{itemize}
\vspace{-0.5em}
\vspace{-0.5em}
%======================
% Projects
%======================
\section*{Projects}
\vspace{-0.8em}
\rule{\linewidth}{2pt}
\textbf{NASA Collaboration: Space Biology Research}

\textit{NemaLife inc.}
 \vspace{-0.8em}
\begin{itemize}
    \item Provided video annotations to track the health of the C. \textit{elegans} and how they responded on different microchips.
     \vspace{-0.8em}
    \item Coordinated with 10 other data analysts to ensure all data was correctly organized into Excel Spreadsheets.
\end{itemize}
 \vspace{-0.8em}
 \textbf{Cellular Automaton Simulator}
 
 \textit{Multiprocessing}
  \vspace{-0.8em}
 \begin{itemize}
     \item Developed in Python this simulator performs iterations on files containing matrices full of cells represented by certain characters and returns the final matrix to the terminal and a new output file. \vspace{-0.8em}
     \item Integrates Python's multiprocessing library for parallelizing row-wise matrix generations after out-of-bounds index wrapping with Modulo Arithmetic. \vspace{-0.8em}
     \item Utilizes mathematical conditions and algorithms for determining the next state of the cell for the next iteration. \vspace{-0.8em}
 \end{itemize}

\textbf{Front-end Compiler}

\textit{Lexical Analyzer}
\vspace{-0.8em}
\begin{itemize}
    \item Developed in C this Lexical Analyzer preforms tokenization on 26 lexemes using deterministic finite automaton logic.\vspace{-0.8em}
    \item Implements whitespace and newline handling to track the line of the file to ensure no matter what is on the file the data will be accurately analyzed. \vspace{-0.8em}
    \item Flexible enough to run on its own without the Syntax Parser in an IDE or with a Makefile to read the given file and return it as tokens defined in the token.h file.
\end{itemize}
\vspace{-0.8em}
\textit{Syntax Parser}
\vspace{-0.8em}
\begin{itemize}
    \item Developed in C this Syntax Parser implements the Lexical Analyzer to add the function of letting the user know if there is a syntax error and what line the error is occurring on.
    \vspace{-0.8em}
    \item This Syntax Parser accounts for the left-wise recursion problem in the BNF rules of Cooke's Programming Language.\vspace{-0.8em}
    \item Integrated a custom built Makefile to compile faster in a Linux server environment when dealing with very large files.
\end{itemize}

\vspace{-0.5em}
\vspace{-0.5em}
%======================
% Technical Skills
%======================
\section*{Technical Skills}
\vspace{-0.8em}
\rule{\linewidth}{2pt}
\textbf{Programming Languages}
\vspace{-0.8em}
\begin{itemize}
    \item Python, C, Java, Bash, LaTex
\end{itemize}
\vspace{-0.8em}
\textbf{Software Tools}
\vspace{-0.8em}
\begin{itemize}
    \item Excel Spreadsheets, Microsoft Word, Microsoft PowerPoint
\end{itemize}

\end{document}
